---
output:
  html_document:
    theme: null
    highlight: null
    css: styles.css
---

```{r knitr_init, echo=FALSE, cache=FALSE}
library(knitr)

## Global options
opts_chunk$set(echo=FALSE,
	             cache=FALSE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
```

```{r load_packages}
library(tidyverse)
library(readxl)
library(leaflet)
library(leaflet.extras)
library(rgdal)
```

```{r load_bounds, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# colours
col_rc_grey_light = "#9CAAAE"
col_rc_green_dark = "#05853A"
col_rc_teal = "#2B7586"
col_nhs_orange = "#ED8B00"

load("deprivation.RData")

max_ppl = max(lsoas_access@data$People, lsoas_crime@data$People, lsoas_education@data$People, lsoas_employment@data$People, lsoas_environment@data$People,
              lsoas_health@data$People, lsoas_housing@data$People, lsoas_housing_access@data$People, lsoas_imd@data$People, lsoas_income@data$People)

pal = colorNumeric("Reds", c(0, max_ppl))
pal_ruc = colorFactor(c(col_nhs_orange, col_rc_green_dark, col_rc_teal), lsoas_imd@data$RUC)
```

```{r icons, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
shop_icon = awesomeIcons(
  icon = 'fa-shopping-basket',
  iconColor = 'black',
  library = 'fa',
  markerColor = "lightblue",
  squareMarker = F
)

shop_closed_icon = awesomeIcons(
  icon = 'fa-shopping-basket',
  iconColor = 'black',
  library = 'fa',
  markerColor = "lightred",
  squareMarker = F
)

shop_soon_icon = awesomeIcons(
  icon = 'fa-shopping-basket',
  iconColor = 'black',
  library = 'fa',
  markerColor = "lightgreen",
  squareMarker = F
)
```

<!--html_preserve-->
<style type="text/css">
.tg  {border-collapse:collapse;border-spacing:0;border:none;}
.tg td{padding:1px 5px;border-style:solid;border-width:0px;overflow:hidden;word-break:normal;}
.tg .tg-us36{border-color:inherit;vertical-align:top}
</style>

<div style="z-index: 1; position: absolute; top: 0px; left: 50px; background-color: rgba(255, 255, 255, 0.6); padding: 5px 5px 5px 5px; font-size: 12px">
  <h3>Domains of deprivation</h3>
  <p>This map shows the 10% most deprived areas of the UK for each domain of deprivation.</p>
  <p>Note that deprivation is defined differently in each of the UK nations, so they cannot be directly compared.</p>
</div>
<!--/html_preserve-->

```{r map}
leaflet(lsoas_imd,
        width = "100%", height = "100%", padding = 0,
        options = leafletOptions(minZoom = 5, maxZoom = 12, attributionControl = T)) %>% 
  
  # centre map on Whitendale Hanging Stones, the centre of GB: https://en.wikipedia.org/wiki/Centre_points_of_the_United_Kingdom
  setView(lat = 54.00366, lng = -2.547855, zoom = 7) %>%
  addProviderTiles(providers$CartoDB.Positron) %>% 
  
  # overall IMD
  addPolygons(data = lsoas_imd,
              weight = 1, smoothFactor = 0.5, fillOpacity = 1,
              # color = col_rc_red, fillColor = col_rc_red,
              # color = ~pal(People), fillColor = ~pal(People),
              color = ~pal_ruc(RUC), fillColor = ~pal_ruc(RUC),
              highlightOptions = highlightOptions(color = col_rc_grey_light, weight = 2, bringToFront = T),

              label = ~Name,

              popup = ~paste(
                "<b>", Name, "</b><br/><br/>",
                "Breakdown of deprivation domains<br/>",
                "Overall IMD decile: ", IMD_decile, "<br/>",
                "Income decile: ", Income_decile, "<br/>",
                "Education decile: ", Education_decile, "<br/>",
                "Health decile: ", Health_decile, "<br/>",
                "Crime decile: ", Crime_decile, "<br/>",
                "Environment decile: ", Environment_decile, "<br/>",
                "<br/>",
                "Housing and access decile: ", Housing_and_Access_decile, "<br/>",
                "Housing decile: ", Housing_decile, "<br/>",
                "Access decile: ", Access_decile, "<br/>"
              ),
              group = "Overall deprivation") %>%
  
  # income
  addPolygons(data = lsoas_income,
              weight = 1, smoothFactor = 0.5, fillOpacity = 1,
              # color = col_rc_red, fillColor = col_rc_red,
              # color = ~pal(People), fillColor = ~pal(People),
              color = ~pal_ruc(RUC), fillColor = ~pal_ruc(RUC),
              highlightOptions = highlightOptions(color = col_rc_grey_light, weight = 2, bringToFront = T),

              label = ~Name,

              popup = ~paste(
                "<b>", Name, "</b><br/><br/>",
                "Breakdown of deprivation domains<br/>",
                "Overall IMD decile: ", IMD_decile, "<br/>",
                "Income decile: ", Income_decile, "<br/>",
                "Education decile: ", Education_decile, "<br/>",
                "Health decile: ", Health_decile, "<br/>",
                "Crime decile: ", Crime_decile, "<br/>",
                "Environment decile: ", Environment_decile, "<br/>",
                "<br/>",
                "Housing and access decile: ", Housing_and_Access_decile, "<br/>",
                "Housing decile: ", Housing_decile, "<br/>",
                "Access decile: ", Access_decile, "<br/>"
              ),
              group = "Income deprivation") %>%
  
  # education
  addPolygons(data = lsoas_education,
              weight = 1, smoothFactor = 0.5, fillOpacity = 1,
              # color = col_rc_red, fillColor = col_rc_red,
              # color = ~pal(People), fillColor = ~pal(People),
              color = ~pal_ruc(RUC), fillColor = ~pal_ruc(RUC),
              highlightOptions = highlightOptions(color = col_rc_grey_light, weight = 2, bringToFront = T),

              label = ~Name,

              popup = ~paste(
                "<b>", Name, "</b><br/><br/>",
                "Breakdown of deprivation domains<br/>",
                "Overall IMD decile: ", IMD_decile, "<br/>",
                "Income decile: ", Income_decile, "<br/>",
                "Education decile: ", Education_decile, "<br/>",
                "Health decile: ", Health_decile, "<br/>",
                "Crime decile: ", Crime_decile, "<br/>",
                "Environment decile: ", Environment_decile, "<br/>",
                "<br/>",
                "Housing and access decile: ", Housing_and_Access_decile, "<br/>",
                "Housing decile: ", Housing_decile, "<br/>",
                "Access decile: ", Access_decile, "<br/>"
              ),
              group = "Education deprivation") %>%
  
  # health
  addPolygons(data = lsoas_health,
              weight = 1, smoothFactor = 0.5, fillOpacity = 1,
              # color = col_rc_red, fillColor = col_rc_red,
              # color = ~pal(People), fillColor = ~pal(People),
              color = ~pal_ruc(RUC), fillColor = ~pal_ruc(RUC),
              highlightOptions = highlightOptions(color = col_rc_grey_light, weight = 2, bringToFront = T),

              label = ~Name,

              popup = ~paste(
                "<b>", Name, "</b><br/><br/>",
                "Breakdown of deprivation domains<br/>",
                "Overall IMD decile: ", IMD_decile, "<br/>",
                "Income decile: ", Income_decile, "<br/>",
                "Education decile: ", Education_decile, "<br/>",
                "Health decile: ", Health_decile, "<br/>",
                "Crime decile: ", Crime_decile, "<br/>",
                "Environment decile: ", Environment_decile, "<br/>",
                "<br/>",
                "Housing and access decile: ", Housing_and_Access_decile, "<br/>",
                "Housing decile: ", Housing_decile, "<br/>",
                "Access decile: ", Access_decile, "<br/>"
              ),
              group = "Health deprivation") %>%
  
  # crime
  addPolygons(data = lsoas_crime,
              weight = 1, smoothFactor = 0.5, fillOpacity = 1,
              # color = col_rc_red, fillColor = col_rc_red,
              # color = ~pal(People), fillColor = ~pal(People),
              color = ~pal_ruc(RUC), fillColor = ~pal_ruc(RUC),
              highlightOptions = highlightOptions(color = col_rc_grey_light, weight = 2, bringToFront = T),

              label = ~Name,

              popup = ~paste(
                "<b>", Name, "</b><br/><br/>",
                "Breakdown of deprivation domains<br/>",
                "Overall IMD decile: ", IMD_decile, "<br/>",
                "Income decile: ", Income_decile, "<br/>",
                "Education decile: ", Education_decile, "<br/>",
                "Health decile: ", Health_decile, "<br/>",
                "Crime decile: ", Crime_decile, "<br/>",
                "Environment decile: ", Environment_decile, "<br/>",
                "<br/>",
                "Housing and access decile: ", Housing_and_Access_decile, "<br/>",
                "Housing decile: ", Housing_decile, "<br/>",
                "Access decile: ", Access_decile, "<br/>"
              ),
              group = "Crime deprivation") %>%
  
  # environment
  addPolygons(data = lsoas_environment,
              weight = 1, smoothFactor = 0.5, fillOpacity = 1,
              # color = col_rc_red, fillColor = col_rc_red,
              # color = ~pal(People), fillColor = ~pal(People),
              color = ~pal_ruc(RUC), fillColor = ~pal_ruc(RUC),
              highlightOptions = highlightOptions(color = col_rc_grey_light, weight = 2, bringToFront = T),

              label = ~Name,

              popup = ~paste(
                "<b>", Name, "</b><br/><br/>",
                "Breakdown of deprivation domains<br/>",
                "Overall IMD decile: ", IMD_decile, "<br/>",
                "Income decile: ", Income_decile, "<br/>",
                "Education decile: ", Education_decile, "<br/>",
                "Health decile: ", Health_decile, "<br/>",
                "Crime decile: ", Crime_decile, "<br/>",
                "Environment decile: ", Environment_decile, "<br/>",
                "<br/>",
                "Housing and access decile: ", Housing_and_Access_decile, "<br/>",
                "Housing decile: ", Housing_decile, "<br/>",
                "Access decile: ", Access_decile, "<br/>"
              ),
              group = "Environment deprivation") %>%
  
  # housing and access
  addPolygons(data = lsoas_housing_access,
              weight = 1, smoothFactor = 0.5, fillOpacity = 1,
              # color = col_rc_red, fillColor = col_rc_red,
              # color = ~pal(People), fillColor = ~pal(People),
              color = ~pal_ruc(RUC), fillColor = ~pal_ruc(RUC),
              highlightOptions = highlightOptions(color = col_rc_grey_light, weight = 2, bringToFront = T),

              label = ~Name,

              popup = ~paste(
                "<b>", Name, "</b><br/><br/>",
                "Breakdown of deprivation domains<br/>",
                "Overall IMD decile: ", IMD_decile, "<br/>",
                "Income decile: ", Income_decile, "<br/>",
                "Education decile: ", Education_decile, "<br/>",
                "Health decile: ", Health_decile, "<br/>",
                "Crime decile: ", Crime_decile, "<br/>",
                "Environment decile: ", Environment_decile, "<br/>",
                "<br/>",
                "Housing and access decile: ", Housing_and_Access_decile, "<br/>",
                "Housing decile: ", Housing_decile, "<br/>",
                "Access decile: ", Access_decile, "<br/>"
              ),
              group = "Housing and access deprivation") %>%
  
  # housing
  addPolygons(data = lsoas_housing,
              weight = 1, smoothFactor = 0.5, fillOpacity = 1,
              # color = col_rc_red, fillColor = col_rc_red,
              # color = ~pal(People), fillColor = ~pal(People),
              color = ~pal_ruc(RUC), fillColor = ~pal_ruc(RUC),
              highlightOptions = highlightOptions(color = col_rc_grey_light, weight = 2, bringToFront = T),

              label = ~Name,

              popup = ~paste(
                "<b>", Name, "</b><br/><br/>",
                "Breakdown of deprivation domains<br/>",
                "Overall IMD decile: ", IMD_decile, "<br/>",
                "Income decile: ", Income_decile, "<br/>",
                "Education decile: ", Education_decile, "<br/>",
                "Health decile: ", Health_decile, "<br/>",
                "Crime decile: ", Crime_decile, "<br/>",
                "Environment decile: ", Environment_decile, "<br/>",
                "<br/>",
                "Housing and access decile: ", Housing_and_Access_decile, "<br/>",
                "Housing decile: ", Housing_decile, "<br/>",
                "Access decile: ", Access_decile, "<br/>"
              ),
              group = "Housing deprivation") %>%
  
  # access
  addPolygons(data = lsoas_access,
              weight = 1, smoothFactor = 0.5, fillOpacity = 1,
              # color = col_rc_red, fillColor = col_rc_red,
              # color = ~pal(People), fillColor = ~pal(People),
              color = ~pal_ruc(RUC), fillColor = ~pal_ruc(RUC),
              highlightOptions = highlightOptions(color = col_rc_grey_light, weight = 2, bringToFront = T),

              label = ~Name,

              popup = ~paste(
                "<b>", Name, "</b><br/><br/>",
                "Breakdown of deprivation domains<br/>",
                "Overall IMD decile: ", IMD_decile, "<br/>",
                "Income decile: ", Income_decile, "<br/>",
                "Education decile: ", Education_decile, "<br/>",
                "Health decile: ", Health_decile, "<br/>",
                "Crime decile: ", Crime_decile, "<br/>",
                "Environment decile: ", Environment_decile, "<br/>",
                "<br/>",
                "Housing and access decile: ", Housing_and_Access_decile, "<br/>",
                "Housing decile: ", Housing_decile, "<br/>",
                "Access decile: ", Access_decile, "<br/>"
              ),
              group = "Access deprivation") %>%
  
  addLayersControl(
    overlayGroups = c("Overall deprivation", "Income deprivation", "Education deprivation", "Health deprivation", "Crime deprivation",
                      "Environment deprivation", "Housing and access deprivation", "Housing deprivation", "Access deprivation"),
    options = layersControlOptions(collapsed = FALSE)
  ) %>%

  addLegend("bottomright", pal = pal_ruc,
            values = ~RUC,
            title = "Rural/urban classification",
            opacity = 1
  ) %>%
  
  hideGroup("Income deprivation") %>% 
  hideGroup("Education deprivation") %>% 
  hideGroup("Health deprivation") %>% 
  hideGroup("Crime deprivation") %>% 
  hideGroup("Environment deprivation") %>% 
  hideGroup("Housing and access deprivation") %>% 
  hideGroup("Housing deprivation") %>% 
  hideGroup("Access deprivation")
```
